AMORPH: A statistical program for characterizing amorphous materials by X-ray diffraction

### 2018-03-25 doc/ms.tex
Minor edits

\begin{table}
\footnotesize
\centering
\begin{tabular}{|llll|}
\hline
{\bf X-ray Anode}      &   {\bf X-ray wavelength}   &  {\bf Control point 2} & {\bf Control point 3}\\
 &   {\bf (\AA)}   &  {\bf(\degree 2 theta)} & {\bf(\degree 2 theta)}\\
\hline
Cr & 2.29 & 15.0 & 61.2\\
Fe & 1.94 & 12.7 & 51.1\\
Co & 1.79 & 11.7 & 46.9\\
{\bf Cu} & {\bf 1.54} & {\bf 10.0} & {\bf 40.0}\\
Mo & 0.71 & 4.6 & 18.2\\
Ag & 0.56 & 3.6 & 14.3\\
\hline
\end{tabular}
\caption{\it Typical XRD anodes with recommended background control points based on a predominant 8.8-2.25 {\AA}  amorphous peak.\label{tab:anode}}
\end{table}

>>>>

\begin{table}
\footnotesize
\centering
\begin{tabular}{|llll|}
\hline
{\bf X-ray Anode}      &   {\bf X-ray wavelength}   &  {\bf Control point 2} & {\bf Control point 3}\\
 &   {(\AA)}   &  {\bf(\degree $2\theta$)} & {\bf(\degree $2\theta$)}\\
\hline
Cr & 2.29 & 15.0 & 61.2\\
Fe & 1.94 & 12.7 & 51.1\\
Co & 1.79 & 11.7 & 46.9\\
{\bf Cu} & {\bf 1.54} & {\bf 10.0} & {\bf 40.0}\\
Mo & 0.71 & 4.6 & 18.2\\
Ag & 0.56 & 3.6 & 14.3\\
\hline
\end{tabular}
\caption{\it Typical XRD anodes with recommended background control points based on a predominant 8.8--2.25 {\AA}  amorphous peak.\label{tab:anode}}
\end{table}
